A Computational Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-03-29 paper/paper.tex

\subsubsection{Comparison to our proposed theory}
On the surface, a common point between the FEP and our proposed RL-based framework
  is placing the minimization of a surprise signal at the core of brain function.
  Indeed in RL, surprise minimization is subsumed  by accurate prediction of
  rewarding outcomes in the future. A ``free-energy'' agent is barely a biomechanical machine which has the tendency to resist internal phase-transitions which lead contradictory with the
  blurred version of the external world captured as sensations
  \citep{friston2010free,fristonAIorRL,ortega2013thermodynamics}. Such a theory cannot by itself,
  explain the emergence of strategic behavior inherent in humans (e.g cite dark-room experiment).

>>>>

\subsubsection{Comparison to our proposed theory}
On the surface, a common point between the FEP and our proposed RL-based framework
  is placing the minimization of a surprise signal at the core of brain function.
  Indeed in RL, surprise minimization is subsumed  by accurate prediction of
  rewarding outcomes in the future. A ``free-energy'' agent is barely a biomechanical machine which has the tendency to resist undesired / harmful phase-transitions.
  \citep{friston2010free,fristonAIorRL,ortega2013thermodynamics}. Such a theory cannot by itself,
  explain the emergence of strategic behavior inherent in humans (e.g cite dark-room experiment).
